\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-11-28 redaction/JEGeo/revision_JEGeo/referees/answers/Answer_referee2.tex

%\newcommand{\note}[1]{\footnote{\begin{doublespace}#1\end{doublespace}}}

\begin{document}

\title{\textsc{International Transport costs:\\New Findings from modeling additive costs} \\
Answer to Referee 2}

%\author{Guillaume \textsc{Daudin}\thanks{%
%Université Paris Dauphine, PSL University, LEDa-DIAL, UMR CNRS 8805-UMR IRD 260, 75016, Paris, France ; email: \url{guillaume.daudin@dauphine.psl.eu}}  \qquad J\'{e}r\^{o}me \textsc{H\'{e}ricourt} \thanks{Corresponding author. Universit\'{e} de Lille - LEM-CNRS UMR 9221, France \& CEPII, France; email: \url{jerome.hericourt@univ-lille.fr}}\qquad Lise \textsc{Patureau}\thanks{
%University Paris Dauphine, PSL University, LEDa-DIAL, UMR CNRS 8805-UMR IRD 260, 75016 Paris, France;  email: \url{lise.patureau@dauphine.psl.eu} } }

### 2021-11-29 redaction/JEGeo/revision_JEGeo/referees/answers/Answer_referee1.tex

%\newcommand{\note}[1]{\footnote{\begin{doublespace}#1\end{doublespace}}}

\begin{document}

\title{\textsc{International Transport costs:\\New Findings from modeling additive costs} \\
Answer to Referee 1}

%\author{Guillaume \textsc{Daudin}\thanks{% Université Paris Dauphine, PSL University, LEDa-DIAL, UMR CNRS 8805-UMR IRD 260, 75016, Paris, France ; email: \url{guillaume.daudin@dauphine.psl.eu}}  \qquad J\'{e}r\^{o}me \textsc{H\'{e}ricourt} \thanks{Corresponding author. Universit\'{e} de Lille - LEM-CNRS UMR 9221, France \& CEPII, France; email: \url{jerome.hericourt@univ-lille.fr}}\qquad Lise \textsc{Patureau}\thanks{ University Paris Dauphine, PSL University, LEDa-DIAL, UMR CNRS 8805-UMR IRD 260, 75016 Paris, France;  email: \url{lise.patureau@dauphine.psl.eu} } }

### 2021-11-29 redaction/JEGeo/revision_JEGeo/revised_article/DHP_JoEG_rev1.tex

\title{\textsc{International Transport costs:\\New Findings from modeling additive costs}\thanks{We thank the referees, as well as the editor, William Kerr, for insightful comments, which helped to significantly improve the paper. We are grateful to Holger G\"{o}rg, S\'{e}bastien Jean and Vincent Vicard for their critics and suggestions on earlier drafts. The paper has also greatly benefited from remarks from the participants at ETSG 17\textsuperscript{th} (Helsinki), DEGIT XXII (Paris), seminars at the universities of California-Irvine, Paris-Dauphine, Paris-I and Nancy and the Kiel Institute for the World Economy. Any remaining errors are ours. This paper was partly funded by a university grant from the University of Lille. It features an online appendix containing additional results, available on the authors' websites and on \url{https://github.com/gdaudin/trade_costs}.}}

>>>>

\title{\textsc{International Transport costs:\\New Findings from modeling additive costs}\thanks{%We thank the referees, as well as the editor, William Kerr, for insightful comments, which helped to significantly improve the paper. 
We are grateful to Holger G\"{o}rg, S\'{e}bastien Jean and Vincent Vicard for their critics and suggestions on earlier drafts. The paper has also greatly benefited from remarks from the participants at ETSG 17\textsuperscript{th} (Helsinki), DEGIT XXII (Paris), seminars at the universities of California-Irvine, Paris-Dauphine, Paris-I and Nancy and the Kiel Institute for the World Economy. Any remaining errors are ours. This paper was partly funded by a university grant from the University of Lille. It features an online appendix containing additional results, available on the authors' websites%and on \url{https://github.com/gdaudin/trade_costs}
.}}

### 2021-11-29 redaction/JEGeo/revision_JEGeo/revised_article/Online_Appendix/online_appendix_DHP_rev1.tex

%Modèle additif seul DONE
%+Tableaux avec toutes les années en 3 digit DONE
% Tableaux avec toutes les années en 4 digit ???
%Harmoniser la présentation des résultats (cf table 1 du papier) DONE
%Les résultats sur la version Hummels mais avec sa pondération: en annexe du papier? En online appendix? DONE, mais à compléter

>>>>

\author{Guillaume \textsc{Daudin}\thanks{%
University Paris Dauphine, PSL University, LEDa-DIAL, UMR CNRS 8805-UMR IRD 260, 75016 Paris, France; email: \url{guillaume.daudin@dauphine.psl.eu}}  \qquad J\'{e}r\^{o}me \textsc{H\'{e}ricourt} \thanks{Corresponding author. Univ. Lille, CNRS, IESEG School of Management, UMR 9221 - LEM - Lille Économie Management, F-59000 Lille, France, and CEPII, France; email: \url{jerome.hericourt@univ-lille.fr}}\qquad Lise \textsc{Patureau}\thanks{
University Paris Dauphine, PSL University, LEDa, UMR CNRS 8805- UMR IRD 260, 75016 Paris, France;  email: \url{lise.patureau@dauphine.psl.eu} } }

\date{November 2021}
